Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-03-15 Scripts/evaluating_pca.Rmd
fixed code to save plots in loop

```{r}
fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""))

@@

for(i in 1:length(fileslst)){
  pcadata <- readRDS(fileslst[i])

@@

  #filtering low variance predictors
  nzv <- nearZeroVar(pcadata, saveMetrics= TRUE)
  nzvar <- rownames(nzv[nzv$nzv,])
  if(length(nzvar) > 0){ 
    pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
    }

@@

  ##Plots without loadings
  p <- autoplot(prcomp(pcadata_f[,-(dim(pcadata_f)[2])]),
         #loadings = TRUE,
         label = TRUE, 
         label.size = 3,
         label.repel=T,
         data=pcadata_f,
         colour='Group') +
  theme_bw()

>>>>

```{r}
fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"), "/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""))

@@

for(i in 1:length(fileslst)){
  print(i)
  pcadata <- readRDS(fileslst[i])

@@

  #filtering low variance predictors
  nzv <- nearZeroVar(pcadata, saveMetrics= TRUE)
  nzvar <- rownames(nzv[nzv$nzv,])
  if(length(nzvar) > 0){ 
    pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
    }else{pcadata_f <- pcadata}

@@

  ##Plots without loadings
  p <- autoplot(prcomp(pcadata_f[,-(dim(pcadata_f)[2])]),
         #loadings = TRUE,
         label = TRUE, 
         label.size = 3,
         label.repel=T,
         data=pcadata_f,
         colour='Group',
         label.show.legend = FALSE) +
  theme_bw()
